% OSHA CFR 29 Part 1926 — Binary Reward Function Summary Table
% Include in paper with: \input{osha_table}
% Requires packages: booktabs, xcolor, colortbl, longtable, array, multirow

\definecolor{criticalbg}{HTML}{FDDEDE}
\definecolor{highbg}{HTML}{FEF3CD}
\definecolor{mediumbg}{HTML}{D9EAD3}
\definecolor{lowbg}{HTML}{CFE2F3}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}

\begin{longtable}{@{}l L{2.2cm} L{2.8cm} L{5.5cm} c c c@{}}
\caption{OSHA CFR 29 \S1926 Binary Reward Functions for VLM Egocentric Evaluation.
Each function maps a specific regulation to a yes/no question answerable from a single bodycam frame.
Severity: \textbf{C}ritical, \textbf{H}igh, \textbf{M}edium.}
\label{tab:osha_rewards} \\

\toprule
\textbf{ID} &
\textbf{CFR \S} &
\textbf{Rule Name} &
\textbf{Binary Question (VLM Prompt)} &
\textbf{Cat.} &
\textbf{Sev.} &
\textbf{Verif.} \\
\midrule
\endfirsthead

\multicolumn{7}{c}{{\tablename\ \thetable{} -- continued}} \\
\toprule
\textbf{ID} &
\textbf{CFR \S} &
\textbf{Rule Name} &
\textbf{Binary Question (VLM Prompt)} &
\textbf{Cat.} &
\textbf{Sev.} &
\textbf{Verif.} \\
\midrule
\endhead

\midrule \multicolumn{7}{r}{{Continued on next page}} \\
\endfoot

\bottomrule
\endlastfoot

% ── Fall Protection ───────────────────────────────────────────────────────────
\rowcolor{criticalbg}
RF-001 & 1926.502(d)(16) & PFAS Harness Worn &
Is the worker wearing a full-body fall arrest harness with dorsal D-ring at shoulder level? &
FP & C & \checkmark \\

\rowcolor{criticalbg}
RF-002 & 1926.502(d)(17) & Lanyard Connected &
Is the worker's lanyard/SRL snap hook visibly engaged to a rated anchorage point? &
FP & C & \checkmark \\

\rowcolor{criticalbg}
RF-003 & 1926.502(b)(1) & Guardrail Top Rail &
Is a continuous top rail at 39–45 in.\ present along all unprotected platform edges? &
FP & C & \checkmark \\

\rowcolor{highbg}
RF-004 & 1926.502(j)(1) & Safety Net Below &
Is a compliant safety net installed beneath the work area when PFAS/guardrails are absent? &
FP & H & \checkmark \\

\rowcolor{highbg}
RF-026 & 1926.502(c)(1) & Safety Monitor &
Is a dedicated safety monitor present on the same level, unoccupied by other tasks, with LOS to all workers? &
FP & H & \checkmark \\

\midrule
% ── Scaffolding ───────────────────────────────────────────────────────────────
\rowcolor{criticalbg}
RF-005 & 1926.451(g)(1) & Scaffold Fall Protection &
Are workers on scaffold $>$10 ft behind a complete guardrail system or wearing a connected PFAS? &
SC & C & \checkmark \\

\rowcolor{highbg}
RF-006 & 1926.451(b)(1) & Scaffold Full Planking &
Is the scaffold platform fully planked with no gaps $>$1 in.\ and no missing or broken planks? &
SC & H & \checkmark \\

\rowcolor{highbg}
RF-007 & 1926.451(e)(1) & Scaffold Proper Access &
Are workers accessing the scaffold via a ladder or stairway, NOT by climbing cross-bracing? &
SC & H & \checkmark \\

\rowcolor{highbg}
RF-028 & 1926.451(c)(1) & Mudsills \& Base Plates &
Are scaffold base plates and mudsills present under every leg, with scaffold plumb and stable? &
SC & H & \checkmark \\

\midrule
% ── Ladders ───────────────────────────────────────────────────────────────────
\rowcolor{highbg}
RF-008 & 1926.1053(b)(1) & Three-Point Contact &
Is the worker facing the ladder and maintaining $\geq$3 points of contact while climbing? &
LA & H & \checkmark \\

\rowcolor{highbg}
RF-009 & 1926.1053(b)(4) & Portable Ladder Secured &
Is the portable ladder tied/hooked at the top and set at approximately a 75° angle? &
LA & H & \checkmark \\

\rowcolor{mediumbg}
RF-010 & 1926.1053(b)(22) & No Ladder as Walkway &
Is the ladder used only as a climbing device, NOT placed horizontally as a bridge or platform? &
LA & M & \checkmark \\

\rowcolor{mediumbg}
RF-027 & 1926.1053(b)(5)(i) & Stepladder Open/Locked &
Are the stepladder spreaders fully open and locked before the worker climbs? &
LA & M & \checkmark \\

\midrule
% ── PPE ───────────────────────────────────────────────────────────────────────
\rowcolor{criticalbg}
RF-011 & 1926.100(a) & Hard Hat Worn &
Is the worker wearing a hard hat properly positioned on the top of the head? &
PP & C & \checkmark \\

\rowcolor{highbg}
RF-012 & 1926.102(a)(1) & Eye Protection Worn &
Is the worker wearing safety glasses, goggles, or face shield during cutting/grinding/welding? &
PP & H & \checkmark \\

\rowcolor{mediumbg}
RF-013 & 1926.101(a) & Hearing Protection &
Is the worker wearing earplugs or earmuffs when operating loud equipment ($\geq$90 dBA)? &
PP & M & \checkmark \\

\rowcolor{highbg}
RF-014 & 1926.95(a) & Hi-Vis Vest Worn &
Is the worker wearing an ANSI Class 2/3 fluorescent vest near vehicle traffic or equipment? &
PP & H & \checkmark \\

\rowcolor{highbg}
RF-025 & 1926.28(a) & Task-Appropriate PPE &
For the visible hazardous task, is the worker wearing the complete required PPE ensemble? &
PP & H & \checkmark \\

\midrule
% ── Electrical ────────────────────────────────────────────────────────────────
\rowcolor{criticalbg}
RF-015 & 1926.416(a)(1) & Energized Parts Guarded &
Are all exposed energized conductors de-energized, insulated, or behind barriers? &
EL & C & \checkmark \\

\rowcolor{criticalbg}
RF-016 & 1926.404(b)(1)(ii) & GFCI on Temp Power &
Are all temporary receptacles serving portable tools protected by a GFCI device? &
EL & C & \checkmark \\

\rowcolor{highbg}
RF-017 & 1926.416(e)(1) & Extension Cord Intact &
Are all extension cords free of cuts, fraying, tape splices, and exposed conductors? &
EL & H & \checkmark \\

\rowcolor{criticalbg}
RF-029 & 1926.403(b)(2) & Panel Overcurrent Intact &
Is the temp panel cover closed, slots filled, no bypassed breakers, no burn marks? &
EL & C & \checkmark \\

\midrule
% ── Excavations ───────────────────────────────────────────────────────────────
\rowcolor{criticalbg}
RF-018 & 1926.652(a)(1) & Excavation Protected &
Does an excavation $\geq$5 ft deep have sloping, shoring, or a trench box before workers enter? &
EX & C & \checkmark \\

\rowcolor{highbg}
RF-019 & 1926.651(c)(2) & Spoil Pile Setback &
Is the spoil pile set back $\geq$2 ft from the trench edge with no material overhanging? &
EX & H & \checkmark \\

\rowcolor{highbg}
RF-020 & 1926.651(e) & Egress Ladder in Trench &
Is a ladder, ramp, or stairway inside the excavation reachable within 25 ft lateral travel? &
EX & H & \checkmark \\

\rowcolor{highbg}
RF-030 & 1926.651(j)(2) & Warning Barrier at Edge &
Is the excavation perimeter protected by physical barriers (fence, jersey barrier, etc.)? &
EX & H & \checkmark \\

\midrule
% ── Steel Erection ────────────────────────────────────────────────────────────
\rowcolor{criticalbg}
RF-021 & 1926.753(c)(1) & Decking Sequentially Secured &
Is metal decking placed sequentially with no overhanging panels, fastened before workers walk on it? &
SE & C & \checkmark \\

\rowcolor{criticalbg}
RF-022 & 1926.760(a)(1) & Connector PFAS Connected &
Is each ironworker making connections at $>$15 ft wearing a connected PFAS or positioning device? &
SE & C & \checkmark \\

\midrule
% ── Housekeeping ──────────────────────────────────────────────────────────────
\rowcolor{mediumbg}
RF-023 & 1926.25(a) & Work Area Clear of Debris &
Is the work area and passageway clear of protruding nails, scrap lumber, and tripping hazards? &
HK & M & \checkmark \\

\rowcolor{mediumbg}
RF-024 & 1926.25(b) & Combustible Scrap Removed &
Is combustible scrap cleared from the work zone and not accumulated near ignition sources? &
HK & M & \checkmark \\

\end{longtable}

\vspace{0.5em}
\noindent\textbf{Category codes:}
FP~=~Fall Protection (§1926.500–503),\;
SC~=~Scaffolding (§1926.450–454),\;
LA~=~Ladders (§1926.1050–1060),\;
PP~=~PPE (§1926.28, §1926.95–107),\;
EL~=~Electrical (§1926.400–449),\;
EX~=~Excavations (§1926.650–652),\;
SE~=~Steel Erection (§1926.750–761),\;
HK~=~Housekeeping (§1926.25).
\textbf{Sev.:} C~=~Critical, H~=~High, M~=~Medium.
All 30 functions are binary (reward $\in \{0,1\}$) and \textbf{Verif.}~=~\checkmark indicates no human judgment required beyond VLM visual inference.
